FocalGstar

### 2017-06-15 analysis.Rmd
wmatrix images

## Demo: Variable weight matrix (blur)
### Weight matrix sizes
```{r}
r <- rast[[ZOOMLEVEL]]
wsizes <- (1:12)*2 + 5
wsizes
```

```{r blur-wmatrices, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
for(ws in wsizes) {
  w <- weight_matrix_circular_fade(ws, 0)
  w[is.na(w)] <- 0 # removing any NAs from the weight matrix
  plot_weight_matrix(w, show.minmax = FALSE)
}
```

@@

  g <- GetisOrd(r, w, st)
  plot_zscore(g,
              title = sprintf("Focal G*: wsize=%d", ws),
              sigma_thresh = 2)
  writeRaster(g,
              sprintf("data/blur/focalgstar-%dx%d-z%02d-w%02d.tif",
                      nrow(r), ncol(r), ZOOMLEVEL, ws),
              overwrite = TRUE)
}
```
## Example of Parent-Child Clumping Difference
```{r metric-example, message=FALSE, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
r <- rast[[ZOOMLEVEL]]
st1 <- GetisOrdStandardStats(r)
st2 <- GetisOrdLocalStats(r, weight_matrix_circular(FOCAL_MATRIX_SIZE))
plot_clumping_diff(r, st1, ZOOM_WMATRIX_SIZE, 29)
plot_clumping_diff(r, st2, ZOOM_WMATRIX_SIZE, 29)
```

>>>>

## Demo: Variable weight matrix (blur)
### Weight matrix sizes
```{r}
r <- rast[[ZOOMLEVEL]]
wsizes <- (1:12)*2 + 5
wsizes # printed

# selection to be rendered for latex inclusion
RENDERED_IDX <- floor(seq(1, length(wsizes), length.out = 8))
```

We render `r length(RENDERED_IDX)` weight matrices that will be included into a LaTeX document. In order to do this, we selected indices `r RENDERED_IDX`:
```{r blur-wmatrices, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
for (ws in wsizes[RENDERED_IDX]) {
  w <- weight_matrix_circular_fade(ws, 0)
  w[is.na(w)] <- 0 # removing any NAs from the weight matrix
  plot_weight_matrix(w, show.minmax = FALSE)
}
```

@@

  g <- GetisOrd(r, w, st)
  plot_zscore(g,
              title = sprintf("Focal G*: wsize=%d", ws),
              sigma_thresh = 2)
  writeRaster(g,
              sprintf("data/blur/focalgstar-%dx%d-z%02d-w%02d.tif",
                      nrow(r), ncol(r), ZOOMLEVEL, ws),
              overwrite = TRUE)
}
```

## Example of Parent-Child Clumping Difference
```{r metric-example, message=FALSE, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
r <- rast[[ZOOMLEVEL]]
st1 <- GetisOrdStandardStats(r)
st2 <- GetisOrdLocalStats(r, weight_matrix_circular(FOCAL_MATRIX_SIZE))
plot_clumping_diff(r, st1, ZOOM_WMATRIX_SIZE, 29)
plot_clumping_diff(r, st2, ZOOM_WMATRIX_SIZE, 29)
```
